Containers and R: the Rockerverse and beyond

### 2019-10-07 manuscript.Rmd
part about {dockerfiler}

- [`rize` for Shiny](https://github.com/cole-brokamp/rize)
- [`dockerfiler`](https://github.com/ColinFay/dockerfiler)

>>>>

- [`rize` for Shiny](https://github.com/cole-brokamp/rize)

One of the key tool of Docker are dockerfiles, which can be thought of as "recipes" used to build a specific image. 
But building these files can feel like a workflow break as it demands to open a separate file, and / or to write a small wrapper around R's `write()` function to add elements to the file. 
At the same time, doing it by hand prevents from using programming language for what they are good for: iteration, and automation. 
Iteration and automation for Dockerfiles is the very reason behind [`dockerfiler`](https://github.com/ColinFay/dockerfiler), an R package designed for building Dockerfiles straigth from R.

For example, the [`golem`](https://github.com/ThinkR-open/golem) package (an R package for building production-grade Shiny application) makes an heavy use of `dockerfiler` when it comes to creating the `Dockerfile` for deploying the Shiny application to production. 
The reason behind this is that `dockerfiler`, on top of being scriptable from R, can leverage all the tools available in R to parse a `DESCRIPTION` file, to get system requirements, to list dependencies, versions, etc.
